Stage-Splitting a Modal Language

### 2014-10-10 paper/relatedwork.tex
related work...

>>>>

\paragraph{Intro.}

A predominating theme in the design, implementatation, and
optimization of algorithm and software is frequency reduction and
precomputation.  The idea is to reduce the frequency of computations
by reducing their frequency and ideally by precomputing when possible.

The reason for why this theme is as predominant as it is that it is
naturally common in many actual applications.  For example, we may
have a collection of names or numbers that we frequently lookup, as
for example part of a membership test as part of a larger system.  In
some applications areas such as in graphics (the motivation for our
work), this is so common that there is a relatively large literature
on speeding up graphics computations by taking advantage of frequency
reduction and precomputation.

One way to express frequency of computations is to allow the
programmer to stage computation explicitly by making explicit the
stage of each computation and then by moving computations between
stages to improve efficiency by performing work as early (to save time
later when performance might be more critical) and  as infrequently
as possible (to reduce overall time).

For example, in meta-programming~\cite{}, the programmer can assign a
program expression a stage (stage 1, 2, 3, ...), which indicates the
stage at which that expression evaluates.  Combined with the ability
for earlier stages to construct expressions of later stages,
meta-programming techniques can be used to construct efficient
programs that improve efficiency over their non-staged counterparts by
reducing frequency reduction and precomputation.  For example, the
programmer can write a program that takes a list of numbers $\ell$ as
a first stage value and returns a second-stage function that performs
a fast membership test on that list $\ell$ by inlining all the
comparisons.  When given a key to lookup in the second stage, the
membership test function would quickly return the result.
